Object-Oriented Internet\\ Cloud Interoperability

### 2021-01-06 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Final review of the latex text #37
- refactored headers of the tex files.

The remainder of this paper is structured as follows. Sect.~\ref{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model. It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context. A reference implementation of this archetype is described in Sect.~\ref{sect.gateway-implementation}. The most important findings and future work are summarized in Sect.~\ref{section.conclusion}.

@@

\section{Azure - OOI Implementation}\label{sect.gateway-implementation}

>>>>

The remainder of this paper is structured as follows. Sect.~\ref{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model. It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context. A reference implementation of this archetype is described in Sect.~\ref{section.gateway-implementation}. The most important findings and future work are summarized in Sect.~\ref{section.conclusion}.

@@

\section{Azure - OOI Implementation}\label{section.gateway-implementation}
